Balsa: A Compact Line Notation Based on SMILES

### 2022-07-08 manuscript.tex
Clarifies gratuitous selection.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{gratuitous-selection.pdf}
    \caption{Gratuitous selection. These heteroatoms are selected but don't need to be because subvalence is zero in every case. When such atoms are selected, they must be pruned before processing the DS.}
    \label{fig:gratuitous-selection}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{gratuitous-selection.pdf}
    \caption{Gratuitous selection. Heteroatoms are selected needlessly because subvalence is zero in every case. Atoms selected gratuitously, must be pruned before processing the DS.}
    \label{fig:gratuitous-selection}
\end{figure}
